shrimp_goby_boatnoise

### 2025-03-04 ms_boatnoise_shrimp_goby.Rmd
Updating annotations and readability of the code. Also, I have changed the folder structure for better organisation.

prior_model <- brm(
  prior_formula,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 1000, warmup = 100,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1,
  sample_prior = "only",
  file = "prior_check"
)

@@

🚧 Jack, you might consider wiring the brms models to a folder called '4-mods' 🚧

```{r}
# goby_out_model <- brm(
#   goby_out_formula_1,
#   data = final_df,
#   family = zero_one_inflated_beta(),
#   prior = priors,
#   control = list(adapt_delta = 0.99,
#                  max_treedepth = 12),
#   chains = 4, iter = 4000, warmup = 1000,
#   cores = 4, threads = threading(2),
#   backend = "cmdstanr",
#   seed = 1,
#   file = "goby_out_model"
# )
```

@@

```{r}
goby_out_model <-  readRDS(file = "goby_out_model.rds")
```

@@

```{r}
goby_out_plot3
ggsave("./2-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figs/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
```

### Effects of covariates on the proportion of time gobies spent outside of the burrow

@@

```{r}
# shrimp_out_model <- brm(
#   shrimp_out_formula,
#   data = final_df,
#   family = zero_one_inflated_beta(),
#   prior = priors,
#   control = list(adapt_delta = 0.99,
#                  max_treedepth = 12),
#   chains = 4, iter = 4000, warmup = 1000,
#   cores = 4, threads = threading(2),
#   backend = "cmdstanr",
#   seed = 1,
#   file = "shrimp_out_model"
# )
```

@@

```{r}
shrimp_out_model <-  readRDS(file = "shrimp_out_model.rds")
```

@@

shrimp_out_plot3
ggsave("./2-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figs/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
```

### Effects of covariates on the proportion of time shrimp spent outside of the burrow

@@

```{r}
shrimp_contact_model <- brm(
  bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
     ),
  data = final_df,
  prior = priors,
  family = zero_one_inflated_beta(),
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
  file = "shrimp_contact_model"
)

summary(shrimp_contact_model)
```

@@

shrimp_contact_fig_together
ggsave("./2-figs/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

```{r}
shrimp_contact_plot3
ggsave("./2-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figs/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
```

### Modelling the effect of covariates on the proportion of time spent in contact

>>>>

#Now we run and save the model. **unhash** the code below if you haven't downloaded the saved model 'goby_out_model.rds' in the "3-models" folder.

# prior_model <- brm(
#   prior_formula,
#   data = final_df,
#   family = zero_one_inflated_beta(),
#   prior = priors,
#   control = list(adapt_delta = 0.99,
#                  max_treedepth = 12),
#   chains = 4, iter = 1000, warmup = 100,
#   cores = 4, threads = threading(2),
#   backend = "cmdstanr",
#   seed = 1,
#   sample_prior = "only",
#   file = "./3-models/prior_check"
# )

prior_model <-  readRDS(file = "./3-models/goby_out_model.rds")

@@

```{r}
# goby_out_model <- brm(
#   goby_out_formula_1,
#   data = final_df,
#   family = zero_one_inflated_beta(),
#   prior = priors,
#   control = list(adapt_delta = 0.99,
#                  max_treedepth = 12),
#   chains = 4, iter = 4000, warmup = 1000,
#   cores = 4, threads = threading(2),
#   backend = "cmdstanr",
#   seed = 1,
#   file = "./3-models/goby_out_model"
# )
```

@@

```{r}
goby_out_model <-  readRDS(file = "./3-models/goby_out_model.rds")
```

@@

```{r}
goby_out_plot3
ggsave("./2-figures/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figures/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
```

### Estimating the effects of covariates on the proportion of time gobies spent outside of the burrow

@@

```{r}
# shrimp_out_model <- brm(
#   shrimp_out_formula,
#   data = final_df,
#   family = zero_one_inflated_beta(),
#   prior = priors,
#   control = list(adapt_delta = 0.99,
#                  max_treedepth = 12),
#   chains = 4, iter = 4000, warmup = 1000,
#   cores = 4, threads = threading(2),
#   backend = "cmdstanr",
#   seed = 1,
#   file = "./3-models/shrimp_out_model"
# )
```

@@

```{r}
shrimp_out_model <-  readRDS(file = "./3-models/shrimp_out_model.rds")
```

@@

shrimp_out_plot3
ggsave("./2-figures/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figures/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
```

### Estimating the effects of covariates on the proportion of time shrimp spent outside of the burrow

@@

⏭️ **Skip this step** if you have downloaded the saved model 'shrimp_contact_model.rds'. You will load the model in the next step.

```{r}
# shrimp_contact_model <- brm(
#   bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
#      phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
#      zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
#      coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
#      ),
#   data = final_df,
#   prior = priors,
#   family = zero_one_inflated_beta(),
#   control = list(adapt_delta = 0.99, max_treedepth = 12),
#   chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
#   file = "./3-models/shrimp_contact_model"
# )
```

```{r}
shrimp_contact_model <-  readRDS(file = "./3-models/shrimp_contact_model.rds")
```

```{r}
summary(shrimp_contact_model)
```

@@

shrimp_contact_fig_together
ggsave("./2-figures/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

```{r}
shrimp_contact_plot3
ggsave("./2-figures/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figures/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
```

### Estimating the effect of covariates on the proportion of time spent in contact
